%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

% \lastupdated % Print the Last Updated text at the top right

\begin{minipage}[t][0.2\textheight][t]{\textwidth}

\namesection{}{Lena Volzhina}{ % Your name
\urlstyle{same}\url{https://github.com/LenaVolzhina} \\ % Your website, LinkedIn profile or other web address
\href{mailto:LenaVolzhina@ya.ru}{LenaVolzhina@ya.ru} | +372~5619~4358 \\  % Your contact information
Tallinn, Estonia
}


\section{Summary} 

\begin{flushleft}
I am a senior data scientist with solid mathematical background and 6+ years of experience.
\\
Also, I am a regular speaker \href{https://github.com/LenaVolzhina/personal}{[link]} and a member of women tech communities.
\end{flushleft}
\sectionspace
\end{minipage}

%----------------------------------------------------------------------------------------
%   LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t][0.75\textheight][t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 
\sectionspace

\subsection{Saint Petersburg}
\subsection{State University}
\location{2012 – 2018}
\sectionspace
\location{Master's degree with honors \\ in Computer Science \& Engineering}


\sectionspace
%------------------------------------------------

\subsection{Computer Science Center}
\location{2014 – 2017}
\sectionspace

\location{Full list of modules is \href{https://compscicenter.ru/students/734/}{[here]}, including: }
Algorithms~and~Data~Structures \\
Mathematical~Statistics \\
Big~Data \\
Parallel~Programming \\
C++ \\
Java \\
Python


\sectionspace

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}
\sectionspace

\subsection{Technologies}
\sectionspace

    Python~(advanced,~Django)
    \\
    C++~(basic)
    \\
    Machine~learning
    \\
    Data~visualization
    \\
    SQL
    \\
    Jupyter
    \\
    Git
    \\
    Scrum
    \\
    Docker

\sectionspace
\subsection{Core skills}
\sectionspace

    Attention~to~detail
    \\
    Communication
    \\
    Documentation
    \\
    Mentoring
    \\
    Presentation~skills

\sectionspace
\subsection{Languages}
\sectionspace

    English~C1
    \\
    Russian~Native
    \\
    German~B1


\sectionspace

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%   RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t][0.75\textheight][t]{0.6\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}
\sectionspace

\runsubsection{Yandex.Maps}
\\\descript{Senior Data Scientist}
\location{2021 – current time}
\sectionspace

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item My task at Yandex.Maps is to personalize search results for map-related queries using the user data.
\item Currently, I run a series of experiments from scratch: collect and check training and verification pools, set up the pipelines, check a variety of hypoteses, run offline and online experiments. For that project I collaborate with several teams.
\item Most of the infrastructure is written in C++, so I got some production experience, both with development and with complex systems debugging.
\end{tightitemize}

\sectionspace

%------------------------------------------------

\runsubsection{Yandex.Weather}
\\\descript{Data Scientist}
\location{2017 – 2021}
\sectionspace

\begin{tightitemize}
\item At Yandex.Weather, I was using machine learning methods to make weather forecasts.
\item There were large datasets from forecast providers for analysis and processing, so I needed to use various big data technics such as MapReduce paradigm. The purpose of my work was to improve the quality of daily weather forecasts.
\item Mentorship: I have been providing guidance and feedback for two mentees.
\item I also supported and developed Python code that regularly calculates weather forecasts around the world.
\end{tightitemize}

\sectionspace
%------------------------------------------------

\runsubsection{Educational Platform Stepik}
\\\descript{Python Developer~/~Data Analyst}
\location{2015 – 2017}
\sectionspace

\begin{tightitemize}
\item At Stepik, I was involved in various data analysis tasks, mostly related to content recommendations. 
\item I designed and implemented a rule-based recommender system for educational content. Later I worked on an adaptive recommender system, that uses knowledge graph and psychometric models for the most efficient learning. 
\item Also, during my time at Stepik, I completed many separate backend tasks using the Django framework, including but not limited to the implementation of data analysis algorithms described above.
\end{tightitemize}

\sectionspace

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%   SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}